A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-03-19 controlled_study.tex
save space from screenshots

\begin{figure*}[t]
\begin{center}
\fbox{\includegraphics[width=\linewidth,height=2.5in,keepaspectratio]{original.png}}
\end{center}
\caption{Screenshot of the original WordPress REST API documentation}
\label{fig:original}
\end{figure*}

\begin{figure*}[tb]
\begin{center}
\fbox{\includegraphics[width=\linewidth,height=2.5in,keepaspectratio]{forked.png}}
\end{center}
\caption{Screenshot of the enhanced WordPress REST API documentation with a usage example}
\label{fig:enhanced}
\end{figure*}

>>>>

\begin{figure*}[htp]
\centering

\begin{subfigure}[t]{4in}
\centering
\includegraphics[width=4in]{original.png}
\caption{Original API Documentation}
\label{fig:original}
\end{subfigure}
~
\begin{subfigure}[t]{3in}
\centering
\includegraphics[width=2.7in]{forked.png}
\caption{Usage Example from the Enhanced API Documentation}
\label{fig:enhanced}
\end{subfigure}
\caption{Screenshots of Original vs. Enhanced API Documentation}
\end{figure*}
